From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-08-06 WOLFHPC15/article/evaluation.tex
evaluations helene 06_08

The MSL program of FullSWOF contains three mesh entities, seven computation domains, fourty-eight data and ninty-eight computations composed of thirty-two stencil kernels and sixty-six local computations.

@@

Figure~\ref{fig:exectime} illustrates the execution time for each step of the MSC transformation for an overall execution time of ten seconds. Execution times have been computed on a laptop with a bi-core Intel Core i5 1,4 GHz, and 8Gb LPDDR3.

\begin{figure}[!h]
 \begin{center}
 \begin{tabular}{c|c|c|c|c|}
   step & $\Gamma_{sync}$ & $\Gamma_{dep}$ & $\Gamma_{msp}$ & $\Gamma_{tsp}$\\
   \hline
   time (ms) & 2 & 530 & 8297 & 1133\\
   \hline
   \% & 0.02 & 5.3 & 83.3 & 11.37\\
 \end{tabular}
\caption{Execution times of the MSC transformation steps}
\label{fig:exectime}
 \end{center}
\end{figure}

One can notice that the transformation of $\Gamma_{dep}$ to a minimal series-parallel graph is the longest step of MSC, because of the removal of the forbidden shapes in the graph. Actually, the number of forbidden shapes removed in $\Gamma_{dep}$ is not counted, because the algorithm uses a general solution instead of finding each forbidden shape, but it seems that many of them appeared. The \emph{N-shape}, represented in Figure~\ref{fig:n} is forbidden in a minimal series-parallel graph as it is not possible to exactly express it using sequences and parallel sections.
The fact that many \emph{N-shape} are removed in $\Gamma_{dep}$ shows that the creation of a static shedule of tasks may not be the best solution for complex simulations. Actually, if a \emph{N-shape} cannot be represented by sequences and parallel sections, this shape can perfectly be handled by a dynamic scheduler or by the direct static representation of $\Gamma_{dep}$ where tasks wait for their input before starting.

\begin{itemize}
\item speedup Figures
\item number of lines (counting computation components)
\end{itemize}

>>>>

\subsection*{Compiler Evaluation}

@@

Figure~\ref{fig:exectime} illustrates the execution time for each step of the MSC transformation for an overall execution time of ten seconds. Execution times have been computed on a laptop with a bi-core Intel Core i5 1,4 GHz, and 8Gb LPDDR3. 
\begin{figure}[!h]
 \begin{center}
 \begin{tabular}{c|c|c|c|c|}
   step & $\Gamma_{sync}$ & $\Gamma_{dep}$ & $\Gamma_{msp}$ & $\Gamma_{tsp}$\\
   \hline
   time (ms) & 2 & 530 & 8297 & 1133\\
   \hline
   \% & 0.02 & 5.3 & 83.3 & 11.37\\
 \end{tabular}
\caption{Execution times of the MSC transformation steps}
\label{fig:exectime}
 \end{center}
\end{figure}
One can notice that the transformation of $\Gamma_{dep}$ to a minimal series-parallel graph is the longest step of MSC, because of the removal of the forbidden shapes in the graph. Actually, the number of forbidden shapes removed in $\Gamma_{dep}$ is not counted, because the algorithm uses a general solution instead of finding each forbidden shape, but it seems that many of them appeared. The \emph{N-shape}, represented in Figure~\ref{fig:n} is forbidden in a minimal series-parallel graph as it is not possible to exactly express it using sequences and parallel sections.
The fact that many \emph{N-shape} are removed in $\Gamma_{dep}$ shows that the creation of a static shedule of tasks may not be the best solution for complex simulations. Actually, if a \emph{N-shape} cannot be represented by sequences and parallel sections, this shape can perfectly be handled by a dynamic scheduler or by the direct static representation of $\Gamma_{dep}$ where tasks wait for their input before starting.

\subsection*{Preliminary Performances}
To evaluate if performances of the overall automatic parallelization are promising we have proceeded as follows. Our current implementation of the MSCAC compiler generates a back-end code using the SkelGIS library. For this reason, our evaluation compare the shallow water equations first parallelized with a pure SkelGIS code (data structures, applicators and interfaces of SkelGIS~\cite{CPE:CPE3494}), and second parallelized with MSL (which uses the SkelGIS data structure). As the SkelGIS library has proved its scalability on the Shallow water equations compared to an MPI parallelization, the evaluation is relevant to evaluate scalability of MSL. 
Moreover, as SkelGIS library handles data parallelization for distributed memory architectures, we have limited for now our evaluations to the fusionned data parallelization of MSCAC (dumped from $\Gamma_{data}$).

\fix{HC : preciser la machine}

Evaluations have been performed on ... . Figure~\ref{fig:times} shows the execution times in seconds as a function of the number of cores. Figure~\ref{fig:speedup} illustrates a speedup comparison, using the minimum sequential reference time (which is the MSL sequential time). Finally, Figure~\ref{fig:log2} illustrates the logarithmic scale of execution times as a function of the logarithmic scale of the number of cores.
\begin{figure}[!h]
 \begin{center}
 \begin{tabular}{c|c|c|c|c|c|c}
   cores & 8 & 16 & 32 & 64 & 128 & 256\\
   \hline
   MSL & 998.10 & 544.86 & 285.73 & 139.8 & 76.45 & 48.05\\
   \hline
   SkelGIS & 1324.9 & 638.5 & 371.62 & 197.32 & 117.05 & 64.96\\
 \end{tabular}
\caption{Execution times for the shallow water equations using MSL and SkelGIS (in seconds).}
\label{fig:times}
 \end{center}
\end{figure}
\begin{figure*}
\begin{center}
\subfloat[\label{fig:speedup}]{
\resizebox{8cm}{!}{\includegraphics{./images/speedup.pdf}}
}
\hspace{10pt}
\subfloat[\label{fig:log2}]{
\resizebox{8cm}{!}{\includegraphics{./images/logtime.pdf}}
}
\end{center}
\caption{(a) Speedup comparison, and (b) logarithmic execution times, both for the Shallow water equations, using pure SkelGIS and MSL with the SkelGIS data structure.}
\label{fig:perfs}
\end{figure*}

One can notive that execution times using MSL, which itself uses the SkelGIS distributed data structures, is improved compared to a pure SkelGIS parallelization. Moreover, the scalability stays close to the scalability of SkelGIS even if the makespan is improved.
